---
title: "Untitled"
output: html_document
---

To analyze the output of a webppl program for bayesian data analysis

```{r}
#knitr::opts_knit$set(root.dir="/Users/rxdh/Box Sync/stanford/research/goodman/q&a/modeling")
library(ggplot2)
library(GGally)
library(dplyr)
library(tidyr)
library(coda)
library(purrr)
estimate_mode <- function(s) {
  d <- density(s)
  return(d$x[which.max(d$y)])
}

HPDhi<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","upper"])
}

HPDlo<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","lower"])
}
options("scipen"=10) 
```

### Load in empirical data

```{r message=FALSE}
ps = read.csv("../../../MultiExperiment2/data/MultiExp2_compiled-subject_information.csv",
              sep = ',', header = TRUE)
mturk = read.csv("../../../MultiExperiment2/data/MultiExp2_compiled-mturk.csv",
                 sep=',', header= TRUE) %>%
  mutate(gameID = Answer.id) %>%
  select(workerid, gameID)
d = read.csv("../../../MultiExperiment2/data/MultiExp2_compiled-trials_clean.csv",  
             sep = ',', header = TRUE) %>%
  right_join(mturk, by = 'workerid')
english_ps <- (ps %>% 
               filter(nativeEnglish == "yes"))$workerid
cat("We removed", length(ps$workerid) - length(english_ps), "ps due to language")
#trialsCompleted = d %>% count(workerid) %>% mutate(numCompleted = n)
filteredD = d %>% filter(workerid %in% english_ps) %>% 
       filter(answer != "NA") 
completedGames = (filteredD %>% group_by(gameID) %>% 
                    count(gameID) %>% mutate(numCompleted = n) %>% 
                    filter(numCompleted == 24))$gameID
cat("We removed", length(unique(d$workerid)) - length(completedGames)*2, "games total")
d <- filteredD %>% filter(gameID %in% completedGames) %>% 
     distinct(domain, goal, question, guess, answer, type, gameID)
source("../../../MultiExperiment2/analysis/analysisHelpers.R")
d <- mapWordsToNodes(d)
d_q = d %>% 
      mutate(response = ordered(questionNodes, levels = c("Q1","Q2","Q3","Q4"))) %>%
      mutate(goal = ordered(goalNodes, levels = c("G1", "G2", "G3", "G4"))) %>%
      group_by(domain, type, goal) %>%
      do(getProbsAndCIs(data = ., QorA = 'q', R = 1000, FALSE)) %>%
      select(goal, type, response, domain, count, lower_ci, upper_ci,
             groupSize, empProb) %>%
      ungroup() %>%
      filter(!(type == "equivocal" & (response == "Q3" | response == "Q4"))) %>%
      mutate(domain = factor(domain),
             type = factor(type),
             goal = ordered(goal, levels=c("G1","G2","G3","G4")))
d_a = d %>% 
      mutate(response=ordered(answerNodes,levels=c("A1","A2","A3","A4"))) %>%
      mutate(utterance=ordered(questionNodes,levels=c("Q1","Q2","Q3","Q4"))) %>%
      group_by(domain, type, utterance) %>%
      do(getProbsAndCIs(data = ., QorA = 'a', R = 1000, FALSE)) %>%
      select(utterance, type, response, domain, count, lower_ci, upper_ci,
             groupSize, empProb) %>%
      ungroup() %>%
      mutate(domain = factor(domain),
             type = factor(type),
             utterance = ordered(utterance, levels=c("Q1","Q2","Q3","Q4")))
```

### Model comparison

```{r}
options( scipen = 0 )
options( digits =1)
computeBayesFactor <- function(name) {
  inputFile <- paste0("../../guessingGame/Bayesian/data/", name, '.csv')
  raw <- read.csv(inputFile, sep = ",", row.names = NULL) 
  # BDA result:
  res <- raw %>% 
    filter(parameter %in% c("modelType", 'expPragFlip')) %>% 
    group_by(value) %>% 
    summarize(prob = sum(MCMCprob)) %>%
    spread(value, prob) 
  print(res)
  return(signif(res$true/res$false, 3))
}
# print(paste0('BF (beta = 0, questioner): ',
#              computeBayesFactor("betaZeroQuestioner_Params")))
# print(paste0('BF (beta = 0, answerer): ',
#              computeBayesFactor("betaZeroAnswerer_Params")))
print(paste0('BF (free beta, questioner): ',
             computeBayesFactor("questionerFixedParams")))
print(paste0('BF (free beta, answerer): ',
      computeBayesFactor("answererFixedParams")))
```

Looks like there's a super narrow range where the pragmatic model makes much much better predictions... 

```{r}
examineQuestionerParams <- function(name) {
  inputname <- paste0('../../guessingGame/Bayesian/data/', name, '.csv')
  filteredQparams = read.csv(inputname, sep = ",", row.names = NULL) %>% 
    filter(MCMCprob > 0.0001)
  qparams.samples <- filteredQparams[rep(row.names(filteredQparams), filteredQparams$MCMCprob*1000), 1:2] %>%
    filter(parameter != "modelType") %>% 
    mutate(value = as.numeric(as.character( value)))
  View(qparams.samples)
  qparams.samples %>%
    group_by(parameter) %>%
    summarize(mode = estimate_mode(value),
              md_lo = round(HPDlo(value), 3),
              md_hi = round(HPDhi(value), 3))

  questionParamPosterior <- qparams.samples %>%
    ggplot(aes(x = value))+
      geom_histogram(aes(y=..density..), 
                   data =subset(qparams.samples, parameter == "alpha" ), 
                   binwidth = .25, colour="black", fill="white") +
      geom_histogram(aes(y=..density..), 
                   data=subset(qparams.samples, parameter == "beta"), 
                   binwidth = .05, colour="black", fill="white") +
      geom_density(aes(y=..density..),
                   data =subset(qparams.samples, parameter == "alpha" ), 
                   adjust = 5, alpha=.2, fill="#FF6666")+
      geom_density(aes(y=..density..),
                   data=subset(qparams.samples, parameter == "beta"), 
                   adjust = 5, alpha=.2, fill="#FF6666")+
      facet_wrap(~parameter, scales = 'free') +
      theme_bw()
  print(questionParamPosterior)
  outputName = paste0("../../../writing/2016/journal-manuscript/figures/",
                     name, ".pdf")
  ggsave(outputName, questionParamPosterior, 
         width = 6, height = 3, bg = "transparent")
}
examineQuestionerParams('questioner_pragOnlyParams')
```

```{r}
examineAnswererParams <- function(name) {
  inputname <- paste0('../../guessingGame/Bayesian/data/', name, '.csv')
  filteredAparams<-read.csv(inputname, sep = ",", row.names = NULL) %>%
      filter(MCMCprob > 0.0001) %>% 
      filter(parameter != "modelType") %>%
      mutate(value = as.numeric(as.character( value)))
  View(filteredAparams)
  aparams.toplot <- filteredAparams[rep(row.names(filteredAparams), filteredAparams$MCMCprob*1000), 1:2] 
  
  aparams.toplot %>%
      group_by(parameter) %>%
    summarize(mode = estimate_mode(value),
              md_lo = round(HPDlo(value), 3),
              md_hi = round(HPDhi(value), 3))
  
  
  answererParamPosteriors = ggplot(aparams.toplot, aes(x=value))+
      geom_histogram(aes(y=..density..), 
                     data =subset(aparams.toplot, parameter == "alpha" ), 
                     binwidth = .1, colour="black", fill="white") +
      geom_histogram(aes(y=..density..), 
                     data=subset(aparams.toplot, parameter == "beta"), 
                     binwidth = .025, colour="black", fill="white") +
      geom_density(aes(y=..density..),
                   data =subset(aparams.toplot, parameter == "alpha" ), 
                   adjust = 1, alpha=.2, fill="#FF6666")+
      geom_density(aes(y=..density..),
                   data=subset(aparams.toplot, parameter == "beta"), 
                   adjust = 2, alpha=.2, fill="#FF6666")+
      ggtitle("Answerer Parameter Posteriors") +
      facet_grid(~parameter, scales = 'free') +
      theme_bw()
  print(answererParamPosteriors)
  outputFile <- paste0("../../../writing/2016/journal-manuscript/figures/",
                       name, ".pdf")
  ggsave(outputFile, answererParamPosteriors, 
         width = 6, height = 3)
}
examineAnswererParams('answerer_pragOnlyParams')
```

### Predictives

First, for answerer:

```{r}
generateAnswererPredictiveFit <- function(name, typicality) {
  inputname <- paste0('../../guessingGame/Bayesian/data/', name, '.csv')
  apredictive<-read.csv(inputname, sep = ",", row.names = NULL) 

  if(typicality == 'withoutTypicality') {
    apredictive.samples <- apredictive %>% 
      filter(beta == 0) %>%
      filter(MCMCprob == max(MCMCprob))
  } else {
    apredictive.samples <- filter(MCMCprob > 0.0001) %>% 
      apredictive[rep(row.names(apredictive),
                  apredictive$MCMCprob*1000), 
                  -length(colnames(apredictive))]
  }

  apredictive.samples <- apredictive.samples %>%
    mutate(question = as.character(parameter),
           answer = substr(as.character(value), 1, 
                           nchar(as.character(value)) - 1),
           type = as.character(item1),
           domain = as.character(item2)) %>%
    do(mutate(., answer = vectorizedMapAnswer(type, answer))) %>%
    do(mutate(., question = vectorizedMapQuestion(type, question))) %>%
    mutate(utterance = as.factor(question), response = as.factor(answer)) %>%
    select(type, domain, utterance, response, prob)
  View(apredictive.samples)
  apredictive.pp <- apredictive.samples %>%
    group_by(type, domain, utterance, response) %>%
    summarize(MAP = prob) %>%
              # credHigh = HPDhi(prob),
              #credLow = HPDlo(prob)) %>%
    right_join(d_a, by = c("response", "utterance", "domain", "type"))
  #View(apredictive.pp)
  acor = round(cor(apredictive.pp$MAP, apredictive.pp$empProb), 2)

  answer_plots = (ggplot(apredictive.pp, aes(x = MAP, y = empProb))
    + theme(text = element_text(size = 20),
            axis.text.x = element_text(angle=90, vjust=1))
    + xlab("Model predicted probability")
    + ylim(0,1)
    + ylab("Empirical Probability")
    #+ geom_errorbar(aes(ymax = upper_ci, ymin = lower_ci)) 
    #+ geom_errorbarh(aes(xmax = credHigh, xmin = credLow))
    + geom_point(aes(colour = domain, shape = type))
    + geom_abline(intercept = 0, slope = 1, linetype = "dotted")
    + scale_x_continuous(lim = c(0,1), breaks=c(0,.5,1))
    + ggtitle("Answerer Posterior Predictive")
    + geom_smooth(method = "lm")
    + annotate('text', label = paste0('r =',acor), x= 0.8, y = 0.1, size = 8)
    + coord_fixed() 
    + theme(rect = element_rect(fill = "transparent"), # bg of the panel
            panel.background = element_rect(fill = "transparent",colour = NA),
            plot.background = element_rect(fill = "transparent",colour = NA),
            panel.grid.major = element_blank(), # get rid of major grid
            panel.grid.minor = element_blank(), # get rid of minor grid
            legend.background = element_rect(fill = "transparent",colour = NA),
            legend.box.background = element_rect(fill = "transparent",colour = NA) # get rid of legend panel bg
  ))
  print(answer_plots)
  outputfile <- paste0('../../../writing/2016/journal-manuscript/figures/',
                       name, '.pdf')
  ggsave(outputfile, answer_plots, 
         width = 6, height = 6, bg = "transparent")
}
#generateAnswererPredictiveFit('answerer_PragOnlyPredictives', 'withTypicality')
generateAnswererPredictiveFit('answerer_PragOnlyPredictives', 'withoutTypicality')
```

next, generate predictives for questioner:

```{r}
generateQuestionerPredictiveFit <- function(name) {
  fullname = paste0('../../guessingGame/Bayesian/data/', name, '.csv')
  qpredictive <- read.csv(fullname, sep = ",", row.names = NULL) %>%
    filter(MCMCprob > 0.0001)
  qpredictive.samples <- qpredictive[rep(row.names(qpredictive), 
                                     qpredictive$MCMCprob*1000), 1:5] %>%
    mutate(goal = as.character(parameter), 
           question = as.character(value),
           type = as.character(item1),
           domain = as.character(item2)) %>%
    do(mutate(., goal = vectorizedMapGoal(type, goal))) %>%
    do(mutate(., question = vectorizedMapQuestion(type, question))) %>%
    mutate(goal = as.factor(goal), response = as.factor(question)) %>% 
    select(type, domain, goal, response, prob)
  
  qpredictive.pp <- qpredictive.samples %>%
    group_by(type, domain, goal, response) %>%
    summarize(MAP = estimate_mode(prob),
              credHigh = HPDhi(prob),
              credLow = HPDlo(prob)) %>%
    right_join(d_q, by = c("goal","type","domain","response")) 
  
  qcor <- round(cor(qpredictive.pp$MAP, qpredictive.pp$empProb), 2)
  
  question_plots = (ggplot(qpredictive.pp, aes(x = MAP, y = empProb))
    + theme(text = element_text(size = 20),
            axis.text.x = element_text(angle=90, vjust=1))
    + xlab("Model predicted probability")
    + ylim(0,1)
    + ylab("Empirical Probability")
    #+ geom_errorbar(aes(ymax = upper_ci, ymin = lower_ci)) 
    #+ geom_errorbarh(aes(xmax = credHigh, xmin = credLow))
    + geom_point(aes(colour = domain, shape = type))
    + geom_abline(intercept = 0, slope = 1, linetype = "dotted")
    + scale_x_continuous(lim = c(0,1), breaks=c(0,.5,1))
    + ggtitle("Questioner Posterior Predictive")
    + coord_fixed() 
    + geom_smooth(method = "lm")
    + annotate('text', label = paste0('r =',qcor), x= 0.8, y = 0.1, size = 8)
    + theme(rect = element_rect(fill = "transparent"), # bg of the panel
            panel.background = element_rect(fill = "transparent",colour = NA),
            plot.background = element_rect(fill = "transparent",colour = NA),
            panel.grid.major = element_blank(), # get rid of major grid
            panel.grid.minor = element_blank(), # get rid of minor grid
            legend.background = element_rect(fill = "transparent",colour = NA),
            legend.box.background = element_rect(fill = "transparent",colour = NA)) # get rid of legend panel bg
  )
  print(question_plots)
  outputName = paste0("../../../writing/2016/journal-manuscript/figures/",
                      name, ".pdf")
  ggsave(outputName, question_plots, 
         width = 6, height = 6, bg = "transparent")
}
#generateQuestionerPredictiveFit("betaZeroQuestioner_Predictives")
#generateQuestionerPredictiveFit("fullQuestioner_Predictives")
generateQuestionerPredictiveFit('questionerFixed')
```

Let's look at some specific cases, 

1) compare predictives at the MAP parameter values (alpha=6.25, beta= 0.35, flip=TRUE) with slightly higher (alpha=7.5, beta = 0.35, flip = TRUE) or lower (alpha = 5, beta = 0.35, flip = TRUE)

2) compare predictives at the flip=TRUE MAP (alpha=6.25, beta= 0.35, flip=TRUE) with flip=FALSE MAP (alpha=  11.5, beta = 0.2, flip = FALSE)

```{r}
qpredictiveMAP <-read.csv("guessingGame/Bayesian/data/QuestionerflipTrueMAPPredictives.csv", sep = ",", row.names = NULL) %>% rename(pragMAP = prob) %>%
  left_join(read.csv("guessingGame/Bayesian/data/QuestionerflipTrue_higherPredictives.csv", sep = ",", row.names = NULL),
            by = c("parameter", "item1", "item2", "value")) %>% rename(pragHigher = prob) %>% select(-starts_with("MCMC")) %>%
  left_join(read.csv("guessingGame/Bayesian/data/QuestionerflipTrue_lowerPredictives.csv", sep = ",", row.names = NULL),
          by = c("parameter", "item1", "item2", "value")) %>% rename(pragLower = prob) %>%
  left_join(read.csv("guessingGame/Bayesian/data/QuestionerflipFalseMAPPredictives.csv", sep = ",", row.names = NULL),
          by = c("parameter", "item1", "item2", "value")) %>% rename(explMAP = prob) %>%
  mutate(goal = as.character(parameter), 
         question = as.character(value),
         type = as.character(item1),
         domain = as.character(item2)) %>%
  do(mutate(., goal = vectorizedMapGoal(type, goal))) %>%
  do(mutate(., question = vectorizedMapQuestion(type, question))) %>%
  mutate(goal = as.factor(goal), response = as.factor(question)) %>% 
  select(type, domain, goal, response, pragMAP, explMAP, pragHigher, pragLower) %>%
  right_join(d_q %>% select(goal, type, domain, response, empProb), by = c("goal","type","domain","response")) 

ggpairs(qpredictiveMAP, 5:9, axisLabels = 'none')
cor(qpredictiveMAP$pragMAP, qpredictive$empProb)
cor(qpredictiveMAP$explMAP, qpredictive$empProb)

question_plots = (ggplot(qpredictiveMAP, aes(x = explMAP, y = pragMAP))
  + theme(text = element_text(size = 20),
          axis.text.x = element_text(angle=90, vjust=1))
  + xlab("explicit")
  + ylim(0,1)
  + ylab("pragmatic")
  # + geom_errorbar(aes(ymax = upper_ci, ymin = lower_ci)) 
  # + geom_errorbarh(aes(xmax = credHigh, xmin = credLow))
  + geom_point(aes(colour = domain, shape = type))
  + geom_abline(intercept = 0, slope = 1, linetype = "dotted")
  + scale_x_continuous(lim = c(0,1), breaks=c(0,.5,1))
  + ggtitle("explicit vs. pragmatic")
  + geom_smooth(method = "lm")
  + geom_text(aes(x=.75,y=.25,label=paste("r=",qcor)))
  + theme_bw())
question_plots
#dev.off()
```