---
title: "Untitled"
output: html_document
---

We have data from a saliency prior elicitation task where people see a message like "Click the dog!" and a set of four pictures, which may include more than one dog. 

```{r}
library(dplyr)
library(ggplot2)
library(jsonlite)
setwd("~/Box Sync/stanford/research/goodman/q&a/PriorsExperiment/")
```

```{r}
ps = read.csv("data/priorsExperiment-subject_information.csv")

english_ps = (ps %>%
  filter(language %in% c("english", "English")) %>%
  filter(asses == "Yes"))$workerid

cat("We removed", length(ps$workerid) - length(
        (read.csv("data/priorsExperiment-subject_information.csv") %>%
        filter(language %in% c("english", "English")))$workerid), 
    "ps due to native language")

cat("and", 
    length(
        (read.csv("data/priorsExperiment-subject_information.csv") %>%
         filter(language %in% c("english", "English")))$workerid
    ) - length(
        (read.csv("data/priorsExperiment-subject_information.csv") %>%
        filter(asses == "Yes") %>%
        filter(language %in% c("english", "English")))$workerid
    ), "more due to confusion")

data =  read.csv("data/priorsExperiment-trials.csv") %>%
  filter(workerid %in% english_ps) 

totalCounts = data %>%
  group_by(domain,type,label) %>%
  summarize(total = n()) 

proportions = data %>%
  inner_join(totalCounts) %>%
  group_by(domain,type,label,response) %>%
  summarize(prop = n() / mean(total))
```

Generate json...

```{r}
json = toJSON(proportions, pretty = T)
write(json,file = "../modeling/qa/saliencyKnowledgeEmpirical.json")
```

Some analyses of uniformity

```{r}
chisq.pvals = data %>% 
  count(domain, type, label, response) %>%
  group_by(domain, type, label) %>%
  filter(length(n) > 1) %>%
  do(data.frame(stat = chisq.test(.$n)$p.value)) %>%
  ungroup() %>%
  select(stat)
length(which(chisq.pvals < 0.05/length(chisq.pvals$stat))) / length(chisq.pvals$stat)
```

Now we're going to reanalyze Exp. 2 data using these empirical priors. We have to import stuff first:

```{r}
ps = read.csv("../MultiExperiment2/data/MultiExp2_compiled-subject_information.csv",
              sep = ',', header = TRUE)
mturk = read.csv("../MultiExperiment2/data/MultiExp2_compiled-mturk.csv",
                 sep=',', header= TRUE) %>%
  mutate(gameID = Answer.id) %>%
  select(workerid, gameID)
d = read.csv("../MultiExperiment2/data/MultiExp2_compiled-trials_clean.csv",  
             sep = ',', header = TRUE) %>%
  right_join(mturk, by = 'workerid')
english_ps <- (ps %>% 
               filter(nativeEnglish == "yes"))$workerid
cat("We removed", length(ps$workerid) - length(english_ps), "ps due to language")
#trialsCompleted = d %>% count(workerid) %>% mutate(numCompleted = n)
filteredD = d %>% filter(workerid %in% english_ps) %>% 
       filter(answer != "NA") 
completedGames = (filteredD %>% group_by(gameID) %>% 
                    count(gameID) %>% mutate(numCompleted = n) %>% 
                    filter(numCompleted == 24))$gameID
cat("We removed", length(unique(d$workerid)) - length(completedGames)*2, "games total")
d <- filteredD %>% filter(gameID %in% completedGames) %>% 
     distinct(domain, goal, question, guess, answer, type, gameID)
source("~/Box Sync/stanford/research/goodman/q&a/MultiExperiment2/analysis/analysisHelpers.R")
d <- mapWordsToNodes(d)
d_q = d %>% 
      mutate(response = ordered(questionNodes, levels = c("Q1","Q2","Q3","Q4"))) %>%
      mutate(goal = ordered(goalNodes, levels = c("G1", "G2", "G3", "G4"))) %>%
      group_by(domain, type, goal) %>%
      do(getProbs(data = ., QorA = 'q')) %>%
      select(goal, type, response, domain, count,
             groupSize, empProb) %>%
      ungroup() %>%
      mutate(domain = factor(domain),
             type = factor(type),
             goal = ordered(goal, levels=c("G1","G2","G3","G4")))
d_a = d %>% 
      mutate(response=ordered(answerNodes,levels=c("A1","A2","A3","A4"))) %>%
      mutate(utterance=ordered(questionNodes,levels=c("Q1","Q2","Q3","Q4"))) %>%
      group_by(domain, type, utterance) %>%
      do(getProbs(data = ., QorA = 'a')) %>%
      select(utterance, type, response, domain, count,
             groupSize, empProb) %>%
      ungroup() %>%
      mutate(domain = factor(domain),
             type = factor(type),
             utterance = ordered(utterance, levels=c("Q1","Q2","Q3","Q4")))
```

```{r}
answerModelOutput=read.csv("../modeling/guessingGame/answererPredictionsEmp.csv", 
                            sep = ',') %>% 
  mutate(question = as.character(utterance), 
         answer = as.character(response)) %>%
  do(mutate(., answer = vectorizedMapAnswer(type, answer))) %>%
  do(mutate(., question = vectorizedMapQuestion(type, question))) %>%
  mutate(utterance = as.factor(question), response = as.factor(answer)) %>% 
  select(type, domain, modelLevel, utterance, rationality, response, modelProb)

ansFits = optimalFit(inner_join(d_a, answerModelOutput)) %>%
  select(domain, modelLevel, type, utterance, 
         response, empProb, rationality, modelProb)
```

Now that each of these data sets is in a nice format, we can join them all together and plot their fits:

```{r}
# join them all together
all_ans = d_a %>% 
  inner_join(ansFits, by = c('domain', 'type', 'utterance', 'response', 'empProb')) %>%
  mutate(modelLevel = ordered(modelLevel, 
                          levels = c("literal", "explicit", "pragmatic"))) %>%
  select(type, domain, utterance, response, empProb, modelLevel, modelProb) 

# Since they won't let us annotate nicely...
  
labelDataFrame = all_ans %>% 
   group_by(modelLevel) %>% 
   summarise(correlation = paste("r =", round(cor(empProb, 
                                                  modelProb, method = 'pearson'), 2)))

pdf(file="../writing/2015/journal-manuscript/figures/Exp2EmpPriorAnsFits.pdf",
     width = 7, height = 3)
answer_plots = (ggplot(all_ans, aes(x = modelProb, y = empProb))
  + theme(text = element_text(size = 20),
          axis.text.x = element_text(angle=90, vjust=1))
  + xlab("Model predicted probability")
  + ylim(0,1)
  + ylab("Empirical Probability")
  + geom_point(aes(colour = domain, shape = type))
  + geom_abline(intercept = 0, slope = 1, linetype = "dotted")
  + scale_x_continuous(lim = c(0,1), breaks=c(0,.5,1))
  + ggtitle("Answerer Model Fits (Empirical Priors)")
  + geom_smooth(method = "lm")
  + facet_grid( ~ modelLevel)
  + geom_text(aes(x,y,label=lab),
              data=data.frame(x = .75, y = .25,
                              modelLevel = labelDataFrame$modelLevel,
                              lab = labelDataFrame$correlation))
  + theme_bw())
answer_plots         
dev.off()
```

```{r}
# # first, average over domains
# collapsed_a <- d %>% 
#     mutate(response = ordered(answerNodes,levels=c("A1","A2","A3","A4"))) %>%
#     mutate(utterance = ordered(questionNodes,levels = c("Q1","Q2","Q3","Q4"))) %>%
#     group_by(type, utterance) %>%
#     do(getProbsAndCIs(data = ., QorA = 'a', R = 1000)) %>%
#     mutate(empirical = empProb) %>%
#     select(utterance, type, response, count, lower_ci, upper_ci,
#            groupSize, empirical)
# 
# pragModelPreds = ansFits %>% 
#   group_by(utterance, type, modelLevel, response) %>% 
#   summarize(model = mean(modelProb)) %>% 
#   filter(modelLevel == "pragmatic")
# 
# plottableA = collapsed_a %>% 
#   inner_join(pragModelPreds, by = c('utterance','type','response')) %>%
#   select(utterance, type, response, empirical, model, lower_ci, upper_ci) %>%
#   gather(src, prob, empirical, model) %>% 
#   do(mutate(., lower_ci = ifelse(src == "model", NA, lower_ci))) %>%
#   do(mutate(., upper_ci = ifelse(src == "model", NA, upper_ci)))
# 
# # png('../writing/2015/fyp-report/exp4AnsResults.png',
# #      width = 2000, height=1000,res = 300, pointsize = 12)
# 
# dodge <- position_dodge(width=0.9)
# g <- (ggplot(plottableA, aes(x = response, y = prob, fill = src))
#       + geom_bar(position = dodge, stat = "identity") 
#       + geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci), 
#                       position = dodge, width = .25)
#       + facet_grid(type ~ utterance)
#       + ggtitle("Pragmatic Answerer"))
# g
# # dev.off()
```

Now make the questioner plot

```{r}
questionModelOutput=read.csv("../modeling/guessingGame/questionerPredictionsEmp.csv", sep = ',') %>%
  mutate(goal = as.character(goal),
         question = as.character(response)) %>%
  do(mutate(., goal = vectorizedMapGoal(type, goal))) %>%
  do(mutate(., question = vectorizedMapQuestion(type, question))) %>%
  mutate(goal = as.factor(goal), response = as.factor(question)) %>% 
  select(type, domain, modelLevel, goal, rationality, response, modelProb)

         
questFits = optimalFit(inner_join(d_q, questionModelOutput)) %>%
  select(type, domain, modelLevel, goal, response, empProb, modelProb)
```


```{r}
# join them all together
all_qs = d_q %>% 
  inner_join(questFits, by = c('type', 'domain', 'goal', 'response', 'empProb')) %>%
  mutate(modelLevel = ordered(modelLevel, 
                               levels = c("literal", "explicit", "pragmatic"))) %>%
  select(type, domain, goal, response, empProb, modelLevel, modelProb) 
  #distinct(type, domain, goal, response, modelLevel, modelProb)

# Since they won't let us annotate nicely...
  
labelDataFrame = all_qs %>% 
   group_by(modelLevel) %>% 
   summarise(correlation = paste("r =", round(cor(empProb, 
                                                  modelProb, method = 'pearson'), 2)))

pdf(file="../writing/2015/journal-manuscript/figures/Exp2EmpPriorQuestFits.pdf",
     width = 7, height = 3)
question_plots = (ggplot(all_qs, aes(x = modelProb, y = empProb))
  + theme(text = element_text(size = 20),
          axis.text.x = element_text(angle=90, vjust=1))
#          axis.text.x = element_blank(), axis.ticks = element_blank())
#          plot.margin=unit(c(1,1,-1,1), "cm"))
  + ylim(0,1)
  + xlab("Model Predicted Probability")
  + ylab("Empirical Probability")
  + geom_point(aes(colour = domain, shape = type))
  + ggtitle("Questioner Model Fits (Empirical Prior)")
  + geom_abline(intercept = 0, slope = 1, linetype = "dotted")
  + geom_smooth(method = "lm")
  + facet_grid( ~ modelLevel)
  + geom_text(aes(x,y,label=lab),
              data=data.frame(x = .75, y = .25,
                              modelLevel = labelDataFrame$modelLevel,
                              lab = labelDataFrame$correlation))
  + theme_bw())
question_plots               
dev.off()
```

zoom in on overlapping condition

```{r}
collapsed_q <- d %>% 
    mutate(response = ordered(questionNodes, levels = c("Q1","Q2","Q3","Q4"))) %>%
    mutate(goal = ordered(goalNodes, levels = c("G1", "G2", "G3", "G4"))) %>%
    group_by(goal, type, domain) %>%
    filter(type == "overlapping") %>%
    do(getProbsAndCIs(data = ., QorA = 'q', R = 1000)) %>%
    mutate(empirical = empProb) %>%
    select(goal, domain, type, response, count, lower_ci, upper_ci, 
           groupSize, empirical)

pragModelPreds = questFits %>% 
  group_by(goal, type, modelLevel, domain, response) %>% 
  summarize(pragmaticModel = mean(modelProb)) %>% 
  filter(modelLevel == "pragmatic")

expModelPreds = questFits %>% 
  group_by(goal, type, modelLevel, domain, response) %>% 
  summarize(explicitModel = mean(modelProb)) %>% 
  filter(modelLevel == "explicit")

plottableQ = collapsed_q %>% 
  inner_join(pragModelPreds, by = c('goal', 'type', 'response')) %>%
  inner_join(expModelPreds, by = c('goal', 'type', 'response')) %>%
  select(goal, domain, type, response, lower_ci, upper_ci, groupSize,
         empirical, pragmaticModel, explicitModel) %>%
  gather(src, prob, empirical, pragmaticModel, explicitModel) %>%
  filter(goal == "G2") %>%
  do(mutate(., lower_ci = ifelse(src %in% c("pragmaticModel", "explicitModel"), 
                                 NA, lower_ci))) %>%
  do(mutate(., upper_ci = ifelse(src %in% c("pragmaticModel", "explicitModel"),
                                 NA, upper_ci)))

# png(filename = "../writing/2015/fyp-report/OverlappingModelComparison.png",
#      width = 2000, height=1000,res = 300, pointsize = 16)

(ggplot(plottableQ, aes(x = response, y = prob, fill = src))
 + geom_bar(position = dodge, stat= 'identity')
 + geom_errorbar(aes(ymin = lower_ci, ymax = upper_ci), 
                 position = dodge, width =.25)
 + geom_hline(yintercept = 0.48)
 + ggtitle("Overlapping model comparison")
 + facet_grid(~ domain)
 + theme_bw()
 + scale_fill_manual(values = c("#B2DF8A", "#A6CEE3", "#62A0CA")))
# dev.off()
```

```{r}
library(cocor)
empSet = subset(all_ans, modelLevel == "pragmatic")$empProb
expSet = subset(all_ans, modelLevel == "explicit")$modelProb
pragSet = subset(all_ans, modelLevel == "pragmatic")$modelProb
cocor(~ empirical + expModel | empirical + pragModel, data.frame(empirical = empSet, expModel = expSet, pragModel = pragSet))

empSet = subset(all_qs, modelLevel == "pragmatic")$empProb
expSet = subset(all_qs, modelLevel == "explicit")$modelProb
pragSet = subset(all_qs, modelLevel == "pragmatic")$modelProb
cocor(~ empirical + expModel | empirical + pragModel, data.frame(empirical = empSet, expModel = expSet, pragModel = pragSet))
```