---
title: "R Notebook"
output: html_notebook
---

# Cards experiment

```{r}
library(tidyverse)
library(tidyboot)
```


# Sanity check: number of complete games... 

```{r}
read_csv('../experiments/CardsExperiment/data/chatMessage/chatMessageFromMongo.csv') %>% 
  filter(iterationName == 'single_player_sample') %>% group_by(gameid, trialNum) %>% tally() %>% 
  select(-n) %>% group_by(gameid) %>% tally() %>% filter(n == 6)
```

## Answerer behavior

```{r}
d.subjInfo <- read_csv('../experiments/CardsExperiment/data/exitSurvey/exitSurveyFromMongo.csv') %>% 
  rename(finalRole = role, understandsInstructions = confused) %>% 
  filter(iterationName == 'single_player_sample') %>%
  group_by(gameid) %>% filter(row_number()==1) %>% ungroup()

d.answerer.raw <- left_join(read_csv('../experiments/CardsExperiment/data/reveal/revealFromMongo.csv') %>%
                          group_by(gameid,trialNum) %>% mutate(i = row_number()) %>% 
                          ungroup() %>% filter(sender != 'bot'),
                        d.questioner.raw %>%  select(gameid, trialNum, trialType, target1, target2, distractor1, distractor2, cardAskedAbout, i),
            by = c('gameid', 'trialNum', 'trialType', 'i')) %>% 
  filter(iterationName == 'single_player_sample') %>%
  left_join(d.subjInfo, by = c('gameid')) %>%
  mutate(trialType = factor(trialType, levels = c('catch', 'baseline', 'overlap'), 
                            labels = c('catch', 'baseline', 'overlap'))) %>%
  mutate(revealedObjs = gsub('"|\\[|\\]','',revealedObjs)) %>%
  separate(revealedObjs, into = c('revealed1', 'revealed2')) 

incompleteIDs <- unique((d.answerer.raw %>%
                           group_by(gameid) %>% summarize(trialsComplete = max(trialNum) + 1) %>%
                           filter(trialsComplete != 6))$gameid)
confused_people <- unique((d.answerer.raw %>% 
                             filter(understandsInstructions != 'yes'))$gameid)
nonNative_people <- unique((d.answerer.raw %>% filter(nativeEnglish != 'yes'))$gameid)

catchTrialFail_people <- unique(
  (d.answerer.raw %>% 
   filter(trialType == 'catch') %>% 
   group_by(gameid, trialNum, trialType) %>%
   summarize(revealedIncorrect = !(first(cardAskedAbout) %in% c(first(revealed1), first(revealed2)))) %>%
   filter(revealedIncorrect)
  )$gameid
)

badGames <- unique(c(incompleteIDs, nonNative_people, 
                     confused_people, catchTrialFail_people))

d.answerer <- d.answerer.raw %>%
  filter(!(gameid %in% badGames)) %>%
  group_by(gameid, trialNum, trialType) %>%
  mutate(numRevealed = ifelse(is.na(revealed2), 1, 2)) %>%
  mutate(firstAskedAbout = case_when(
    first(cardAskedAbout) == first(target1) ~ 'target card 1',
    first(cardAskedAbout) == first(target2) ~ 'target card 2',
    first(cardAskedAbout) %in% c(first(distractor1), first(distractor2)) ~ 'distractor', 
    TRUE ~ 'other'
  ))
```

Break out by question being asked... 

```{r}
d.answerer.plot <- d.answerer %>%
  filter(i == 1) %>%
  group_by(gameid, trialNum, trialType) %>%
  mutate(target1Revealed = target1 %in% c(revealed1, revealed2),
         target2Revealed = ifelse(!is.na(target2), target2 %in% c(revealed1, revealed2), TRUE),
         complete = target1Revealed && target2Revealed,
         literal = cardAskedAbout == revealed1 && numRevealed == 1,
         overinf = trialType == 'catch' && numRevealed > 1) %>%
  summarize(answer = case_when(literal ~ 'literal', 
                               overinf ~ 'overinf', 
                               !literal & complete ~ 'pragmatic', 
                               TRUE ~ 'other'),
            cardAskedAbout = first(cardAskedAbout), revealed1 = first(revealed1), revealed2 = first(revealed2),
            targetGoalSet = first(targetGoalSet), distractorGoalSet = first(distractorGoalSet),
            firstAskedAbout = first(firstAskedAbout),
            complete = first(complete), literal = first(literal), target1 = first(target1), target2 = first(target2)) 

d.answerer.boot <- map_dfr(seq_len(1000), ~d.answerer.plot %>%
    group_by(trialType) %>%
    mutate(total = length(answer)) %>%
    do(sample_n(., nrow(.), replace=TRUE)) %>%
    group_by(answer, trialType) %>%
    summarize(prop = length(total)/mean(total), count = length(total)) %>%
    mutate(sample_num = .x)) %>%
    group_by(trialType, answer) %>%
    summarize(mean_prop = mean(prop), ci_upper = ci_upper(prop), ci_lower = ci_lower(prop))
    
ggplot(d.answerer.boot, aes(x = trialType, y = mean_prop, fill = answer)) +
    geom_bar(stat = 'identity') +
    #facet_wrap(~ firstAskedAbout) +
  #geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper), width = 0, position = position_dodge(width = 0.9)) +
    theme_bw() +
    ylim(0,1.1) +
    xlab('trial type') +
    ylab('% responding with answer type')
```

```{r}
d.answerer.plot %>% group_by(trialType, answer) %>% tally()
chisq <- chisq.test(matrix(c(20,22,33,10), nrow = 2))
chisq
```

```{R}
ggplot(d.answerer.boot %>% filter(answer == 'literal'), aes(x = trialType, y = empirical_prop)) +
    geom_bar(stat = 'identity') +
    geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper), width = 0, position = position_dodge(width = 0.9)) +
    theme_bw() +
    scale_fill_few() +
    ylim(0,1) +
    xlab('trial type') +
    ylab('% literal answer') +
    theme(aspect.ratio = 1)

ggsave('../writing/2019/journal-revision/figures/Exp2/answererQualitative.pdf', width=14, height = 10, units='cm')
```

## Questioner behavior

Pre-processing

```{r}
d.questioner.raw <- read_csv('../experiments/CardsExperiment/data/chatMessage/chatMessageFromMongo.csv')  %>% 
  filter(iterationName == 'single_player_sample') %>%
  group_by(gameid, trialNum) %>%   mutate(i = row_number()) %>% ungroup() %>%
  left_join(d.subjInfo, by = c('gameid')) %>%
  mutate(trialType = factor(trialType, levels = c('catch', 'baseline', 'overlap'), 
                            labels = c('catch', 'baseline', 'overlap'))) %>%
  mutate(targetGoalSet = gsub('"|\\[|\\]','',targetGoalSet),
         distractorGoalSet = gsub('"|\\[|\\]','',distractorGoalSet)) %>%
  separate(targetGoalSet, into = c('target1', 'target2'), by = ',', remove = F) %>%
  separate(distractorGoalSet, into = c('distractor1', 'distractor2'), by = ',', remove = F)

d.questioner.raw %>% group_by(gameid) %>% tally()

catchTrialFail_people <- unique((d.questioner.raw %>% 
                                   filter(trialType == 'catch') %>% 
                                   filter(sender == 'human') %>%
                                   group_by(gameid) %>%
                                   summarize(firstIncorrect = first(cardAskedAbout) != first(target1),
                                             numExchanges = n(),
                                             cardAskedAbout = first(cardAskedAbout), 
                                             target1 = first(target1),
                                             distractor1 = first(distractor1)) %>%
                                   filter(firstIncorrect))$gameid)

badGames <- unique(c(incompleteIDs, nonNative_people, confused_people, catchTrialFail_people))

d.questioner <- d.questioner.raw %>%
  filter(!(gameid %in% badGames)) %>%
  filter(sender == 'human') %>%
  group_by(gameid, trialNum, trialType) %>%
  mutate(cardAskedAbout = as.character(cardAskedAbout)) %>%
  summarize(firstAskedAbout = first(cardAskedAbout), firstRole = first(firstRole.x), firstTarget1 = first(target1), firstTarget2 = first(target2), firstDistractor1 = first(distractor1), firstDistractor2 = first(distractor2), timeElapsed = first(timeFromRoundStart)) %>%
  mutate(nameAskedAbout = firstAskedAbout,
         firstAskedAbout = case_when(
           firstAskedAbout == firstTarget1 ~ 'target card 1',
           firstAskedAbout == firstTarget2 ~ 'target card 2',
           firstAskedAbout %in% c(firstDistractor1, firstDistractor2) ~ 'distractor',
           TRUE ~ 'other'
          ))

d.questioner.boot <- map_dfr(seq_len(1000), ~d.questioner %>%
    group_by(trialType) %>%
    filter(firstAskedAbout %in% c('target card 1', 'target card 2')) %>%
    mutate(total = length(firstAskedAbout)) %>%
    do(sample_n(., nrow(.), replace=TRUE)) %>%
    group_by(firstAskedAbout, trialType) %>%
    summarize(prop = length(total)/mean(total)) %>%
    mutate(sample_num = .x)) %>%
    group_by(trialType, firstAskedAbout) %>%
    summarize(empirical_prop = mean(prop), ci_upper = ci_upper(prop), ci_lower = ci_lower(prop))

```

```{r}
d.questioner.boot %>%
  filter(trialType != 'catch') %>%
  filter(firstAskedAbout == 'target card 1') %>%
  ggplot(aes(x = trialType, y = empirical_prop)) +
    geom_bar(stat = 'identity') +
    geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper), width = 0) +
    geom_hline(yintercept = 0.5, linetype = 'dotted') +
    theme_bw() +
    ylim(0,1) +
    xlab('trial type') +
    ylab('% questions about target card') +
    theme(aspect.ratio = 1.33)
  
ggsave('../writing/2019/journal-revision/figures/Exp2/questionerQualitative.pdf', width=14, height = 10, units='cm')
```

NOTE: Should probably do mixed-effects glmer with participant ID random effects 

```{r}
library(BayesianFirstAid)
d.questioner %>%
  group_by(trialType) %>%
  mutate(total = n()) %>%
  group_by(trialType, firstAskedAbout) %>%
  summarize(n = n(), p = n / mean(total))
#chisq <- chisq.test(matrix(c(20,22,33,10), nrow = 2))
proportionBF(33, 43, p = 0.5)
proportionBF(20, 42, p = 0.5)
```

```{r}
d.questioner %>% group_by(gameid, trialNum, trialType) %>% tally() %>% select(-n) %>% group_by(trialType) %>% tally()
```

## Additional analyses

### number of exchanges taken (combined success of questioner/answerer)

Number of exchanges taken on average to complete the goal

```{r}
d.answerer %>%
  group_by(gameid, trialNum, trialType) %>%
  summarize(correct = n() == 1) %>%
  group_by(trialType) %>%
  tidyboot_mean(correct) %>%
  ggplot(aes(x = trialType, y = empirical_stat)) +
    geom_bar(stat = 'identity') +
    geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper), width = 0) +
    theme_bw() +
    coord_cartesian(ylim = c(0, 1)) +
    #ylim(.9, 2) +
    ylab('% success in single exchange')
```

```{r}
summary(lmer(correct ~ trialType + (1 | participantID), data = d.questioner %>%
  group_by(gameid, trialNum, trialType, participantID) %>%
  summarize(correct = n() == 1) %>% 
    filter(trialType != 'catch')
))
contrasts(combined$trialType)
```

### Learning?

```{r}
d.answerer %>%
  group_by(gameid, trialNum, trialType) %>%
  tally() %>%
  rename(numAttempts = n) %>%
  group_by(trialNum) %>%
  tidyboot_mean(numAttempts) %>%
  ggplot(aes(x = trialNum, y = empirical_stat)) +
    geom_line() +
    geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper), width = 0) +
    theme_bw() +
    ylab('# attempts')
```

Check whether some answerers just don't realize they can reveal 2 cards?

```{r}
d.answerer %>%
  group_by(gameid, trialNum, trialType) %>%
  filter(trialType != 'catch') %>%
  summarize(revealedOne = 1 %in% numRevealed) %>%
  group_by(gameid) %>%
  mutate(trialNum = ifelse(trialNum == first(trialNum), 'earlier', 'later')) %>%
  ungroup() %>%
  ggplot(aes(x = trialNum, y = 1, fill = revealedOne, group = interaction(trialNum, trialType))) +
    geom_bar(stat = 'identity') +
    theme_bw() +
    facet_wrap(~ gameid) +
    #ylim(.9, 2) +
    ylab('# attempts')
```

Break out by order effect of having been questioner already?

```{r}
d.questioner %>%
  mutate(firstRole = ifelse(firstRole == 'helper', 'answerer', 'questioner')) %>%
  mutate(firstRole = paste0('first role: ', firstRole)) %>%
  group_by(trialType, firstRole) %>%
  mutate(total = n()) %>%
  group_by(trialType, firstRole, firstAskedAbout) %>%
  summarize(n = n(), p = n / mean(total)) %>%
  ggplot(aes(x = trialType, y = p, fill = firstAskedAbout)) +
    geom_bar(stat = 'identity') +
    theme_few() +
    facet_wrap(~ firstRole) +
    xlab('trial type') +
    ylab('% questions about target card')
```

```{r}
d.questioner %>% filter(firstRole == 'seeker') %>% group_by(trialType, firstAskedAbout) %>% tally()
#chisq <- chisq.test(matrix(c(18,2,7,12), nrow = 2))
prop.test(18, 21, p = 0.5)
proportionBF(18, 20, p = 0.5, rscale = 'medium')
```